\documentclass[12pt]{article}
\usepackage{hyperref}
\title{47 DAYS RF WIZARD}
\author{Shoaib Mustafa}
\begin{document}
\maketitle

\begin{center}
    \section*{DAY 1}
\end{center}
\subsection*{Summary}

I've decided that i'll be documenting my progress in latex as this
will be helpful when i'll be writing thesis. it's also a prettier 
and much more of a sane documenting process considering the mathematical
equations i'll be pushing here. Spent the day setting up environment for setting up latex and 
supporting software, latex is now working. i've learnt The
following commands and decided to test this out. \\
\\
I have gotten in contact with some ham radio enthusiasts on reddit
and Pakistan and they've guided me alot about the physical problems
i'll be facing. I think i'm all set for failing. when i do they are
\\  %This is there to mark the end of line and to switch to a new paragraph. 
\subsection*{Progress}
I'm using this \underline{\href{https://www.cs.princeton.edu/courses/archive/spr10/cos433/Latex/latex-guide.pdf}{Tutorial}}
as reference for practice.
\label{lists} %This is used for referencing later on. we assign it a lablle first and then call it by \ref{lists}
\begin{itemize}
    \item Step-2
    \item Step-3
    \item Step-4
    \item Step-5
\end{itemize}
Here's an enumerated list.
\begin{enumerate}
    \item item1 
    \item item2
    \item item3
    \item item4
\end{enumerate}
%This is a comment. 

Math can be inserted in the following way \\
\begin{center}
    \label{force}
    $F = ma$\\
And \\ $ E = mc^2$ 
%Just beautiful!
\end{center}

This is how you add a table by tabular command.\\
\break
%The output is a bit congested. i wonder how would i make it spacious. 
\begin{tabular}{r|r|r|r|r|cl}
1st column & 2nd column & 3rd column & 4th & 5th\\
\hline a & \ b & c & d & e

\end{tabular}


\end{document}


